---
title: "data608projectproposal"
author: "jim lung"
date: "March 24, 2018"
output:
  html_document: default
  pdf_document: default
---

# Data 608 Project Proposal

## Aim:
** Use of visualization to conduct visual analytics on data analysis **
** Provide answer and question to get the result of analysis **
** Provide user-friendly interface to explore the data as well as find insights from it **

## Methodology:
** Use shiny app provides efficient ways to manipulate and visualize data **
** To explore salary data of 8 professions based on the data about prevailing wage of foreign employers in the United States. The 8 professions include: Data scientist, Software engineers, Data Analyst, Business Analyst, Management Consultant, Assistant Professor, Attorney, Teacher **

## Data source:
** The dataset is from the United States Department of Labor, Employment & Training Administration **
https://www.foreignlaborcert.doleta.gov/performancedata.cfm
** The filtered data for this application contains total 167,278 cases (in 17 columns) in 2015 **
** It is about the prevailing wage data of foreign employers seeking to file applications in the Permanent Labor Certification Program **
** prevailing wage data of US natives are not included **

### Data Glimpse - to deal with NA/missing value
```{r}
library(knitr)
library(dplyr)
library(ggplot2)
library(plotly)
library(sqldf)
library(googleVis)

#x <- read.csv("salary.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
load("salary.Rdata")
head(df)

```

### Cleaning, calculating and re-arrange between job, wage and location
```{r}
arr <- df[,c(8,5)]
colnames(arr) <- c("region", "WAGE")
arr <- aggregate(arr[, 2], list(arr$region), mean)
colnames(arr) <- c("region", "WAGE")
arr$WAGE<-round(arr$WAGE)

salarylevel <- arr %>% arrange(desc(WAGE))
salarylevel

ordered_states <- rev(salarylevel$region)
salarylevel$region <- factor(salarylevel$region, levels = ordered_states)

ggplot(salarylevel, aes(x = region, y = WAGE)) + geom_bar(stat = "identity", alpha = 0.5, col = "blue") + coord_flip() + ggtitle("Wage level per State\n") + scale_y_continuous("Paid Wage") + scale_x_discrete("Region")



```

## We will use the shiny function to compare the wage, job nature and location. 
```{r}
ggplot(df, aes(x=WORK_STATE_ABBREVIATION, y=PAID_WAGE_PER_YEAR, color=JOB_TITLE_SUBGROUP, shape=JOB_TITLE_SUBGROUP)) + geom_point(size=6, alpha=0.6)
```

#### Tools To Be Used:

**GoogleVis**
**Plotly**
**GGplot2**
**Sqldf**

#### Packages To Be Used:

**Plotly**
**Knitr**
**Dplyr**
**Plyr**
**MASS**
**Reshape2**
**Ggplot2**
**Graphics**
**Ggthemes**
**GoogleVis**
**etc**
